Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-24 paper/main.tex
graph; citations

The relative costs and benefits of static vs. dynamic error detection are
well-studied. Despite this, however, many currently-available techniques
are ill-suited to address the problem of localization for type errors in
dynamic languages. First, relying on the extant language interpreter
requires test inputs
(cf.~\cite{Godefroid2005-am,Naylor2007-mi,Cadar2008-kg,PAcheco2007-at}),
may involve error messages that are difficult for novices to
understand~\cite{Marceau2011-ok,Marceau2011-cy,Nienaltowski2008-bv,Jadud2006-ly,Ishii2014-nf},
and may misleadingly implicate the symptom rather than the
cause~\cite{zeller05,Jose2011}.  Second, a
significant amount of development is carried out via IDE or web interfaces,
which require tools that operate on code fragments~\cite{Guo2013-vu}.
Third, attempts to retrofit static type systems into dynamic languages,
such as TypeScript~\cite{typescript2014,refscriptpldi16,mollerOOPSLA14} for
JavaScript and various
gradual and static type approaches for 
Python~\cite{mypy,gradual-typing-python} or
Ruby~\cite{static-typing-ruby,an11,foster09,foster11}
are promising but not always widely
deployed. Finally, research tools and algorithms for fault
localization either require rich static types (e.g., as in
Mycroft~\cite{FIXME}, Nate~\cite{learning-to-blame} or Sherrloc~\cite{FIXME}), require
test cases (e.g., as in Tarantula~\cite{tarantula}), or produce voluminous
ranked output lists that have been found to be unhelpful in general and
less useful to novices in particular~\cite[Sec.~5.1]{orso-parnin}.

@@

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
    ybar,
    symbolic x coords={No Context, No Types},
    xtick=data,
    ymin=0,
    ymax=1.1,
    ylabel=Normalized Model Accuracy,
    enlarge x limits=0.5,
    legend style={at={(0.5,-0.15)},anchor=north}
]
    \addplot table[x=scoreName, y=score, col sep=comma]{removing-features-2-normalized.csv};
    \draw [red] ({rel axis cs:0,0}|-{axis cs:No Types,1}) -- ({rel axis cs:1,0}|-{axis cs:No Types,1}) node [pos=0.33, above] {};
\end{axis}
\end{tikzpicture}
\caption{Normalized accuracy when categories of features are removed, based
on Top-1 decision trees on a random subset of 20,000 program pairs, as
compared to a Top-1 decision tree trained on all features.
\fixme{will add No Syntax bar}
}
\label{fig-removing-features}
\end{figure}

>>>>

The relative costs and benefits of static vs. dynamic error detection are
well-studied. Despite this, however, many currently-available techniques
are ill-suited to address the problem of localization for type errors in
dynamic languages. First, relying on the extant language interpreter
requires test inputs
(cf.~\cite{Godefroid2005-am,Naylor2007-mi,Cadar2008-kg,PAcheco2007-at}),
may involve error messages that are difficult for novices to
understand~\cite{Marceau2011-ok,Marceau2011-cy,Nienaltowski2008-bv,Jadud2006-ly,Ishii2014-nf},
and may misleadingly implicate the symptom rather than the
cause~\cite{zeller05,Jose2011}.  Second, a
significant amount of development is carried out via IDE or web interfaces,
which require tools that operate on code fragments~\cite{Guo2013-vu}.
Third, attempts to retrofit static type systems into dynamic languages,
such as TypeScript~\cite{typescript2014,refscriptpldi16,mollerOOPSLA14} for
JavaScript and various
gradual and static type approaches for
Python~\cite{mypy,gradual-typing-python} or
Ruby~\cite{static-typing-ruby,an11,foster09,foster11}
are promising but not always widely
deployed. Finally, research tools and algorithms for fault
localization either require rich static types (e.g., as in
Mycroft~\cite{MYCROFT-type-errors}, Nate~\cite{learning-to-blame} or Sherrloc~\cite{SHErrLoc}), require
test cases (e.g., as in Tarantula~\cite{tarantula}), or produce voluminous
ranked output lists that have been found to be unhelpful in general and
less useful to novices in particular~\cite[Sec.~5.1]{orso-parnin}.

@@

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
    ybar,
    symbolic x coords={No Context, No Syntax, No Types},
    xtick=data,
    ymin=0,
    ymax=1.1,
    ylabel=Normalized Model Accuracy,
    enlarge x limits=0.3,
    legend style={at={(0.5,-0.15)},anchor=north}
]
    \addplot table[x=scoreName, y=score, col sep=comma]{removing-features-2-normalized.csv};
    \draw [red] ({rel axis cs:0,0}|-{axis cs:No Types,1}) -- ({rel axis cs:1,0}|-{axis cs:No Types,1}) node [pos=0.33, above] {};
\end{axis}
\end{tikzpicture}
\caption{Normalized accuracy when categories of features are removed, based
on Top-1 decision trees on a random subset of 20,000 program pairs, as
compared to a Top-1 decision tree trained on all features.
}
\label{fig-removing-features}
\end{figure}
